Title: Fish do not need Visas: the transboundary nature of world fished species (70/96 character maximum )

### 2019-09-19 Manuscript_Draft.Rmd
updaates

However, incorporating the concept of species distribution has not allays been the case in fisheries management as in the case of EEZs where 90% of wild fish is catched [@]. From 1973 to 1982 the members of the United Nations held a series of meetings to discuss a series of regulations regarding the high seas, a region of international common property, which, at that time, represented waters after 12 miles from shore [@McRae and Munro, 1989]. The third Conference on the Law of the Sea resulted the UN Convention on the Law of the Sea (UNCLOS) which allowed coastal states to claim jurisdiction over 200 nautical mile Exclusive Economic Zones (EEZs) of their coasts [@UN:1982]. Despite intended to improve fisheries management, this arbitrary delimitation of management area had no input from biogeography, ignoring species distributions, and thus creating what we know today as shared stocks. Share stocks, as their name suggest, are fish stocks that live within the waters of two or more nations. The Food and Agricultural Organization of the UN (FAO) recognizes three types: (*i*) transboundary stocks, those stocks that are shared by 2 or more neighboring coastal nations (e.g. Pacific halibu *Hippoglossus stenolepsis*); (*ii*) straddling, those stocks that are shared by two or more nations and also the high seas (e.g. Atlantic cod, *Gadus morhua*); (*iii*) highly migratory stocks; species that are found in the EEZs of coastal nations that are not necessarily neighbors, and the high seas (e.g. all tunas and tuna-like species); and (*iv) discrete high seas stocks; those species that are only found in the high seas.

>>>>

However, incorporating the concept of species distribution has not allays been the case in fisheries management as in the case of EEZs where most of wild fish is catched [@Zeller]. From 1973 to 1982 the members of the United Nations held a series of meetings to discuss a series of regulations regarding the high seas, a region of international common property, which, at that time, represented waters after 12 miles from shore [@McRae and Munro, 1989]. The third Conference on the Law of the Sea resulted the UN Convention on the Law of the Sea (UNCLOS) which allowed coastal states to claim jurisdiction over 200 nautical mile Exclusive Economic Zones (EEZs) of their coasts [@UN:1982]. Despite intended to improve fisheries management, this arbitrary delimitation of management area had no input from biogeography, ignoring species distributions, and thus creating what we know today as shared stocks. Share stocks, as their name suggest, are fish stocks that live within the waters of two or more nations. The Food and Agricultural Organization of the UN (FAO) recognizes three types: (*i*) transboundary stocks, those stocks that are shared by 2 or more neighboring coastal nations (e.g. Pacific halibu *Hippoglossus stenolepsis*); (*ii*) straddling, those stocks that are shared by two or more nations and also the high seas (e.g. Atlantic cod, *Gadus morhua*); (*iii*) highly migratory stocks; species that are found in the EEZs of coastal nations that are not necessarily neighbors, and the high seas (e.g. all tunas and tuna-like species); and (*iv) discrete high seas stocks; those species that are only found in the high seas.
